% My CV's .tex file. Inspired by this one:
% http://www.danielmathews.info/about-me
%
% A pdf version (probably with outdated information, but with the same style)
% can be found here:
% https://blog.erroneousthoughts.org/wp-content/uploads/2012/11/OscarPereiraCV.pdf
%
% WARNING: as it uses custom fonts, this file is supposed to be compiled with
% LuaTeX
%
\documentclass[a4paper,9pt]{extarticle}

%\usepackage[portuguese]{babel}     % i18n
\usepackage[top=2.5cm,left=3cm,right=3cm,bottom=2.5cm]{geometry}
\usepackage[bitstream-charter]{mathdesign}
\usepackage{fontspec}
\setmainfont[Scale=0.9, Ligatures=TeX]{Charis SIL}
\defaultfontfeatures[Charis SIL]{Script=latn}

% This improves the quality of the PDF, but slows down the creation
% time, so you might want to comment it until you have the final version.
\usepackage{microtype}

%%%%%%%%%%%%%

\usepackage{enumitem}
\usepackage{marvosym}
\usepackage{url}
\usepackage[usenames,dvipsnames]{xcolor}  % for MidnightBlue colour
\usepackage[colorlinks=true, urlcolor=MidnightBlue]{hyperref}

\renewcommand\labelitemi{\fontfamily{cmr}\selectfont\textbullet}

\newenvironment{topic}[1]
   {{\noindent\large\bfseries\raisebox{0pt}[\height][1ex]{#1}\hrule}%
    \begin{list}{}{%
       \setlength{\leftmargin}{.0cm}}%
    \item[]}
   {\end{list}\medskip}

\newenvironment{header}[1]
   {\centering{\noindent\large\bfseries\raisebox{0pt}[\height][1ex]{\LARGE\bfseries #1}\hrule}%
    \begin{center}}
   {\end{center}\medskip}

\pagestyle{empty}

\hyphenation{in-fra-struc-ture}

\begin{document}

\begin{header}
  {Óscar Francisco Godinho Pereira} 
  %{\emph{The address and phone number are omitted in this version, due to privacy concerns}}\smallskip\\
  % NOTE: fictional address... for illustrative purposes only.
  { 22nd Baking Steet, Airstrip One, London, Oceania \verb+     + \Telefon +000 12 345 67 89 }\\[5pt]
  \begin{tabular}{l|r}
    \url{https://erroneousthoughts.org} & \texttt{oscar@erroneousthoughts.org} 
  \end{tabular}
\end{header}

\begin{topic}{Professional Experience}
  \begin{itemize}[leftmargin=*]
    \item {\bfseries AnubisNetworks}---Lisbon, Portugal.\\
      Software Engineer (multi-class), June 2007 -- April 2013.
      \begin{itemize}
	\item {\scshape October 2012} -- Moved from product development to the Operations team. Handled 
	  SpamAssassin management and performance tunning. Developed software to 
	  ease (or automate when possible) some of the management tasks, as well spam 
	  statistics collection and analysis.\\
	  {\scshape Requirements}: SpamAssassin, Perl, Apache, RRDTool.
	\item {\scshape June 2011} -- Development of \emph{myFamily} and \emph{Web Protection Service} 
	  web content filtering services. Focus on user interface and authentication modules.\\
	  {\scshape Requirements}: C{}\verb!++!, HTML, CSS, HTTP, tcpflow.
	\item {\scshape May 2009} -- Development of MPS' modules that provide secure and transparent 
	  system administration capabilities\textemdash email infrastructure, et al.---to 
	  ``upper'' layers (business logic). Also developed distributed 
	  alternatives to existing centralised architectural scenarios.\\
	  {\scshape Requirements}: Perl, Postfix, LDAP.
	\item {\scshape June 2007} -- Designed and implemented the Reports module of the \emph{Mail 
	  Protection System}\textsuperscript{\texttrademark} appliance 
	  (MPS)---Anubis' flagship product. Improved the underlying database 
	  scheme to support the required developments. Maintained the web 
	  interface and worked on the initial version of an abstraction layer 
	  aimed at better separating business logic from the underlying system 
	  operations.\\
	  {\scshape Requirements}: Perl, Apache, MySQL.
      \end{itemize}
  \end{itemize}
\end{topic}

\begin{topic}{Formal Education}
  \begin{itemize}[leftmargin=*]
    \item {\bfseries University of Minho}, Braga, Portugal.\\
      M.Sc. Informatics Engineering, 2013--present.
    \item {\bfseries Technical University of Lisbon -- IST}, Lisbon, Portugal.\\
      B.Sc. Applied Mathematics, 2010--present (\emph{currently suspended}).
    \item {\bfseries University of Coimbra}, Coimbra, Portugal.\\
      B.Sc. Informatics Engineering (pre-Bologna -- 5 years), 2001--2007.
  \end{itemize}
\end{topic}

\begin{topic}{Technical Skills}
  {\itshape Programming Languages}  
  \begin{itemize}[leftmargin=*]
    \item{\bfseries Imperative}: \emph{proficient}: C, Perl; \emph{experienced}: C{}\verb!++!, Python;
      \emph{basic skills}: Java, Javascript/JQuery.
    \item{\bfseries Functional}: \emph{basic skills}: Common Lisp.
    \item{\bfseries Markup}: \emph{proficient}: HTML, CSS, \LaTeX; \emph{basic skills}: UML.
  \end{itemize}
  {\itshape Operating Systems} 
  \begin{itemize}[leftmargin=*]
    \item{\bfseries GNU/Linux}: Has been fiddling with different distributions 
      since 2000; became a regular user circa 2005.
      \begin{itemize}
	\item Proficient \textsc{Arch Linux} user (current distribution of choice for personal computers).
	\item Experienced with \textsc{Ubuntu Server} (mainly for small network 
	  servers).
      \end{itemize}
    \item{\bfseries Microsoft Windows}: Last version regularly used was XP (SP3).
  \end{itemize}
  {\itshape Software}
  \begin{itemize}[leftmargin=*]
    \item{\bfseries Text Editors}: Vim (proficient), Kate, KDevelop (IDE).
    \item{\bfseries Mathematics}: Mathematica, Matplotlib, SageMath.
    \item{\bfseries Network}: OpenSSH, tcpflow, iptables, Apache, nginx, RRDTool, GnuPG, 
      Mutt.
    \item{\bfseries Databases}: MySQL, SQLite, PostgreSQL.
  \end{itemize}
\end{topic}

\begin{topic}{Languages}
  \begin{itemize}[leftmargin=*]
    \item {\bfseries Portuguese}: native speaker. (\emph{Note: European 
      Portuguese})
    \item {\bfseries English}: fluent domain, both written and spoken.
    \item {\bfseries Spanish}: fluent speaker, elementary reading and writing skills.
  \end{itemize}
\end{topic}

\newpage   % obviously, comment this if unneeded
\begin{topic}{Additional Information}
  {\itshape Informal Education / Professional Development}\\ 
  {\slshape \small \mbox{\ \ \ \ \ \ \ \ \ \ } Note: only courses completed with certification are listed.}
  \begin{itemize}[leftmargin=*]
    \item {\bfseries Coursera Online Platform}, Stanford University.\\
      Crypto I -- \url{http://www.crypto-class.org} -- 2012
  \end{itemize}
  {\itshape Miscellanea}  
  \begin{itemize}[leftmargin=*]
    \item{Outdoor sports enthusiast---currently surf, football, and trying
      snowboard.}
    \item{Enjoys recreational---and often not-so-recreational---mathematics,
      as well as physics (and chess).}
    \item{Participated in the 2003 and 2004 editions of \emph{Minho Campus
      Party} (Portugal's first large scale LAN party!).}
    \item Writes at \url{https://blog.erroneousthoughts.org} (Portuguese and 
      English). Paraphrasing the Nobel prize winning physicist Richard Feynman: 
      \emph{to explain, one must first understand}. Writing being mostly about 
      the former, it provides a strong incentive to put in the effort needed to 
      achieve the latter. Besides, writing helps one to become a better---and 
      faster!---reader.
    \item The above notwithstanding, he chronically tends to accumulate more books than 
      what he is able to read.
    \item{Full Portuguese driving license---Category B, passenger light
      vehicles.}
  \end{itemize}
\end{topic}

\end{document}
